---
title: "R Objects Workflow and Functions"
format: html
editor: visual
---

#Vectors

Use Ctr+Alt+i to get R markdown box
Create a Vector

```{r}
set.seed(42)
my_unif <- runif(30)
is.vector(my_unif)
```
Subset that object

```{r}
my_unif[1:10]
#combining the values 1-3 and 15-17 using a c function

my_unif [c(1:3, 15:17)]

```

Sort function to sort the vector

```{r}
sort(my_unif)
```

Create a vector with String into it. Sort it, lower case go before upper and number go before everything
```{r}
char_vec <- c('adf', 'daf', 'ced', '13ad', 'Ead', '')
sort(char_vec)
```
#Data Frame

```{r}
data(trees)
trees
str(trees)
```
Subset a Column

```{r}
trees$Height
```
Get attribute from the data frame
```{r}
attributes(trees)

names(trees)
colnames(trees) [2:3]
```
#Lists
Investigating the Data Frame
```{r}

is.list(trees)
is.data.frame(trees)


```
We can subset data frame as a list

```{r}
trees[1] #this will give first column from data frame
trees[[1]] #subset the 1st column as a vector
trees[1:2] #this will give 2 columns
```
Look at linear model fit
```{r}
fit <- lm(Volume ~ Height + Girth, data = trees)

```
Look at structure but restrict info:

```{r}
str(fit,max.level= 1)

```

Some helper function exist

```{r}
fit$coefficients
coef(fit)
```




